### 2016-01-14 paper-arxiv-v2/sec-mva.tex
Added plots of ANN cut to the paper

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It should be emphasized that MVAs such as the ANNs used in this work can always be understood as
a combined set of correlated cuts.
%
Once the ANNs have been trained, it is possible to compare  kinematical distributions after and before the ANN  cut to verify its impact.
%
This information would allow in principle to perform a cut-based analysis, without the need of using ANNs,
and finding similar results.

To illustrate this point,
in Fig.~\ref{fig:pt_H0_sub0_res_noPU_ANNcut} we show
the $p_T$ distribution of the leading AKT04 small-$R$ jets
and the invariant mass of reconstructed Higgs candidates in the resolved
  category, comparing the pre-MVA results ($y_{\rm cut}=0$) with the post-MVA
  results ($y_{\rm cut}=0.60$) for signal and background  events.
  %
  The distributions are not normalized, to better visualize the effect
  of the MVA cut.
  %
  Unsurprisingly, the ANN cut effectively selects events which
  lead to similar kinematical distributions between signal
  and background events.
  %
  In the case of the small-$R$ jets $p_T$ distribution, the
  ANN cuts favors the
  high-$p_T$ region, while for the invariant mass distribution
  only the region around the Higgs mass peak is selected for
  background events.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/pt_H0_sub0_res_noPU_ANNcut.pdf}
\includegraphics[width=0.48\textwidth]{plots/pt_H0_sub0_res_noPU_ANNcut_back_4b.pdf}
\includegraphics[width=0.48\textwidth]{plots/m_H0_res_noPU_ANNcut.pdf}
\includegraphics[width=0.48\textwidth]{plots/m_H0_res_noPU_ANNcut_back_4b.pdf}
\caption{\small
  The $p_T$ distribution of the leading AKT04 small-$R$ jets (upper plots)
  and
  the invariant mass of reconstructed Higgs candidates (lower plots) in the resolved
  category, comparing the pre-MVA results ($y_{\rm cut}=0$) with the post-MVA
  results ($y_{\rm cut}=0.60$) for signal (left) and background (right plot) events.
  %
  In this case the distributions are not normalized, to better visualize the effects
  of the MVA cut.
}
\label{fig:pt_H0_sub0_res_noPU_ANNcut}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
